---
title: "Final Project Classification"
author: "Arash Akhavi"
date: "12/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r}
library(tidyverse)
library(tidymodels)
library(kknn)
library(ROCR)
library(ggplot2)
library(vip)
library(kknn)
library(glmnet)
```
```{r}
cah_train <- read_csv("Data/CAH-201803-train.csv")
cah_test <- read_csv("Data/CAH-201803-test.csv")
head(cah_train)
cah_train <- cah_train %>% 
  mutate(
    #Q1 = as.factor(Q1),
    political_affiliation = as.factor(political_affiliation)
    #Q4 = as.factor(Q4),
    #Q5 = as.factor(Q5),
    #Q6 = as.factor(Q6),
    #Q7 = as.factor(Q7),
    #Q8 = as.factor(Q8),
    #Q9 = as.factor(Q9),
    #Q10 = as.factor(Q10),
    #Q11 = as.factor(Q11),
    #Q12 = as.factor(Q12),
    #Q13 = as.factor(Q13),
   # Q14 = as.factor(Q14),
   # Q15 = as.factor(Q15),
   # Q16 = as.factor(Q16),
   # Q17 = as.factor(Q17),
   # Q18 = as.factor(Q18)
  )

cah_split <- cah_train %>% initial_split()
cah_test1 <- cah_split %>% testing()
cah_train1 <- cah_split %>% training()

cah_cvs <- vfold_cv(cah_train, v = 10)

cah_rec <- recipe(political_affiliation ~ ., cah_train) %>% 
  step_rm(id_num)
```

```{r}
rf_spec <- rand_forest(mtry = tune(), trees = tune(), min_n = tune()) %>%
  set_engine("ranger") %>%
  set_mode("classification")

rf_wflow <- workflow() %>%
  add_recipe(cah_rec) %>%
  add_model(rf_spec)

rf_grid <- control_grid(save_pred = TRUE, verbose = TRUE)

rf_grid_search <-
  tune_grid(
    rf_wflow,
    resamples = cah_cvs,
    control = rf_grid
  )

rf_grid_search %>% 
  show_best(metric = "roc_auc")

# Best RF Metrics
# mtry = 4
# trees = 482
# min_n = 24

rf_mod <- rand_forest(mtry = 4, trees = 482, min_n = 24) %>%
  set_engine("ranger", importance = "impurity")%>%
  set_mode("classification")

rf_wflow <- workflow() %>%
  add_recipe(cah_rec) %>%
  add_model(rf_mod)

rf_fit <- rf_wflow %>% 
  fit(cah_train)

rf_fit %>% 
  pull_workflow_fit() %>% 
  vip(num_features = 10,
      aesthetics = list(color = "black", fill = "indianred")) 
```

```{r}
knn_mod <- nearest_neighbor(neighbors = 100) %>%
  set_engine("kknn") %>%
  set_mode("classification")

cah_rec2 <- recipe(political_affiliation ~ Q4 + Q2 + Q16 + Q17 + Q6 + Q15  + Q13 + Q11, data = cah_train) %>%
  step_normalize(all_numeric())

cah_wflow_knn <- workflow() %>%
  add_recipe(cah_rec2) %>%
  add_model(knn_mod)

cah_fit <- cah_wflow_knn %>%
  fit(cah_train)

cah_wflow_knn %>% 
  fit_resamples(resamples = cah_cvs) %>% 
  collect_metrics()
```
#Confusion Matrix
preds1 <- cah_fit %>% predict(cah_train)

cah_test_k <- cah_train %>%
  mutate(
    pred_output = preds1$.pred_class
  ) 
cah_test_k %>% count(political_affiliation, pred_output)

knn <- cah_test_k %>% 
  accuracy(political_affiliation, pred_output)
knn

cah_fit %>% pull_workflow_fit()
summary(cah_fit)



bag_mod <- bag_tree() %>%
  set_engine("rpart", times = 25) %>%
  set_mode("classification")

bag_tree_wflow <- workflow() %>%
  add_recipe(cah_rec) %>%
  add_model(bag_mod)

bag_tree_wflow %>%
  fit_resamples(resamples = cah_cvs) %>% 
  collect_metrics()

```{r}

cah_rec2 <- recipe(political_affiliation ~ Q4 + Q2 + Q16 + Q17 + Q6 + Q15 + Q10 + Q13 + Q11, data = cah_train) %>%
  step_normalize(all_numeric())


tune_spec <- mlp(
  hidden_units = tune(),
  penalty = tune(),
  epochs = 100,
  activation = "softmax"
) %>%
  set_engine("nnet") %>%
  set_mode("classification")

nn_wflow <- workflow() %>%
  add_recipe(cah_rec2) %>%
  add_model(tune_spec)

nn_grid <- control_grid(verbose = TRUE, save_pred = TRUE)

nn_grid_search <-
  tune_grid(
    nn_wflow,
    resamples = cah_cvs,
    ctrl = nn_grid
  )

nn_grid_search %>%
  show_best(metric = "roc_auc")

# Best NN metrics:
#   hidden_units: 3
#   penalty: 	3.125283e-01

nn_mod <- mlp(
  hidden_units = 3,
  penalty = 	3.125283e-01,
  epochs = 250,                 #Change Epcohs from 100 to 200 to 250
  activation = "linear"
) %>%
  set_engine("nnet") %>%
  set_mode("classification")

nn_wflow <- workflow() %>%
  add_recipe(cah_rec) %>%
  add_model(nn_mod)

nn_wflow %>%
  fit_resamples(resamples = cah_cvs) %>% 
  collect_metrics()

nn_fit <- nn_wflow %>% 
  fit(cah_train)

preds1 <- nn_fit %>% predict(cah_test)
cah_test_fin <- cah_test %>% 
  mutate(
    predicted_value = preds1$.pred_class
  )
```


```{r}
# Create CSV
id_column <- 
  cah_test %>% 
  select(id_num)
fin <- data.frame(id_column, 
                  cah_test_fin$predicted_value)
write.csv(fin,
          "/Users/Arash/Downloads/kaggle1.csv", 
          row.names = FALSE)
```

